Ground state energy of diatomic molecules\\ in the Quantum Drude Oscillator model

### 2022-06-23 paper/main.tex
minor
mathematica file added

@@

\begin{table}[h!]
\caption{\label{tab:table1} Ground state energy (in Ha) of the H-H system}
\begin{ruledtabular}
\begin{tabular}{c|ccc}
        \diagbox[height=1.8\line]{$r$ (a.u.)}{$\tau$ (\textcolor{teal}{unit})}& 0.0 & 1.0 & 2.0\\
        \hline
        1.0 & 5.428021 & 1.000000 & 3.673658 \\
        2.0 & 0.531071 & 0.210137 & 0.872826 \\
        3.0 & 1.532129 & 0.957917 & 0.999836 \\
        4.0 & 1.968642 & 0.999963 & 1.000023 \\
        5.0 & 0.031075 & 1.000000 & 1.014180 \\
        6.0 & 0.978062 & 5.375749 & 0.970292 \\
        7.0 & 21.654276 & 0.558010 & -34.785660 \\
        8.0 & 43.488829 & 85.452632 & -28.868817
\end{tabular}
\end{ruledtabular}
\end{table}

\begin{table}[h!]
\caption{\label{tab:table2} Ground state energy (in Ha) of the He-He system}
\begin{ruledtabular}
\begin{tabular}{c|ccc}
    \diagbox[height=1.8\line]{$r$ (a.u.)}{$\tau$ (\textcolor{teal}{unit})}& 0.0 & 1.0 & 2.0\\
    \hline
    1.0 & 1.000000 & 1.000000 & 5.739538 \\
    2.0 & 1.266281 & 1.134311 & -0.966946 \\
    3.0 & 0.880808 & 0.147328 & -0.206244 \\
    4.0 & 3.755382 & 0.136923 & 1.000000 \\
    5.0 & 1.000000 & 0.999847 & 0.415453 \\
    6.0 & 6.604936 & 1.000000 & -1.709232 \\
    7.0 & 1.000008 & 1.000000 & 9.223832 \\
    8.0& 198.102785 & 1.000000 & 20.246740
\end{tabular}
\end{ruledtabular}
\end{table}

>>>>

\section*{TO DO}

    \begin{itemize}
        \item Talk about the fact that the large coefficients $c_n$ and $d_n$ are polynomials in $\epsilon$ and $S$. In particular, it gives us access to only a finite number of energy levels. In particular $c_n$ is of degree $(\lfloor n/2\rfloor, 1)$ in $(\epsilon, S)$. Solving for $S$ using one of the two equations and plugging back in the other, one gets a rational function of $\epsilon$. The number of zeros is then bounded (some roots might be complex or there could be some simplifications between numerator and denominator) by the degree of the numerator.
    \end{itemize}

@@

\begin{table}[h!]
\caption{\label{tab:table1} Ground state energy (in Ha) of the H-H system}
\begin{ruledtabular}
\begin{tabular}{c|ccc}
    \diagbox[height=1.8\line]{$r$ (a.u.)}{$\mathcal E$ (\textcolor{teal}{unit})}& 0.0 & 1.0 & 2.0\\
    \hline
    1.0 & 5.428021 & 1.000000 & 3.673658 \\
    2.0 & 0.531071 & 0.210137 & 0.872826 \\
    3.0 & 1.532129 & 0.957917 & 0.999836 \\
    4.0 & 1.968642 & 0.999963 & 1.000023 \\
    5.0 & 0.031075 & 1.000000 & 1.014180 \\
    6.0 & 0.978062 & 5.375749 & 0.970292 \\
    7.0 & 21.654276 & 0.558010 & -34.785660 \\
    8.0 & 43.488829 & 85.452632 & -28.868817
\end{tabular}
\end{ruledtabular}
\end{table}

\begin{table}[h!]
\caption{\label{tab:table2} Ground state energy (in Ha) of the He-He system}
\begin{ruledtabular}
\begin{tabular}{c|ccc}
    \diagbox[height=1.8\line]{$r$ (a.u.)}{$\mathcal E$ (\textcolor{teal}{unit})}& 0.0 & 1.0 & 2.0\\
    \hline
    1.0 & 1.000000 & 1.000000 & 5.739538 \\
    2.0 & 1.266281 & 1.134311 & -0.966946 \\
    3.0 & 0.880808 & 0.147328 & -0.206244 \\
    4.0 & 3.755382 & 0.136923 & 1.000000 \\
    5.0 & 1.000000 & 0.999847 & 0.415453 \\
    6.0 & 6.604936 & 1.000000 & -1.709232 \\
    7.0 & 1.000008 & 1.000000 & 9.223832 \\
    8.0& 198.102785 & 1.000000 & 20.246740
\end{tabular}
\end{ruledtabular}
\end{table}
